### 2025-11-17 submissions/03-jpam-RR/manuscript_main.tex
Finish bootstrapping and incorporating the results into the main text

Multinomial logit analyses reveal that anti-Asian bias fundamentally reshapes racial identity choices. I find that when bias increases from its lowest to highest levels, individuals dramatically shift away from ``Asian only'' racial identity, with probabilities decreasing from 98\% to 48\% across all generations, while probabilities of choosing ``White only'' racial identity rise from 1\% to 43\%. In contrast, I find that parental education produces modest and inconsistent effects that vary by family composition: maternal college education increases Asian identity reporting by approximately 11 percentage points among second-generation children of Asian father-White mother families but shows minimal effects in White father-Asian mother families, while paternal education effects remain small across both family types. These patterns suggest that anti-Asian bias, rather than socioeconomic factors, primarily drives identity choices, causing research using subjective measures to misestimate Asian-White gaps in highly prejudiced areas.

@@

In this section, I discuss the results from the multinomial logit analysis. These results reveal how anti-Asian bias differentially affects the probability of choosing ``Asian only,'' ``White only,'' or ``Asian and White'' racial identity, with particularly pronounced effects among mixed-race Asian Americans. Given that the results are mainly driven by individuals with mixed ancestry, I focus the discussion on overall patterns and subsamples with mixed ancestry. The multinomial logit coefficients are in log-odds form, which are difficult to interpret directly. Therefore, I present predicted probabilities to facilitate interpretation.

\textbf{Overall Patterns Among All Generations.} Figure \ref{fig:pp-all-gen} shows predicted probabilities from the multinomial logit model across all generations. Anti-Asian bias produces the most pronounced effects on racial identity choice. When bias increases from its lowest level ($-0.7$) to its highest level ($1.3$), the predicted probability of reporting ``Asian only'' identity decreases dramatically from 98\% to 48\%, while ``White only'' identity increases from 1\% to 43\%, and ``Asian and White'' identity shows a modest increase from 1\% to 8\%. In contrast, gender and parental education produce minimal effects on racial identity choices, with male and female respondents showing virtually identical probabilities across all identity categories, and parental college education generating small, inconsistent effects.

\textbf{Second-Generation Subsample by Parental Composition.} Parental composition reveals substantial differences between Asian father-White mother (AW) and White father-Asian mother (WA) families (Figures \ref{fig:pp-second-aw} and \ref{fig:pp-second-wa}). Among AW families, as bias increases from minimum to maximum levels ($-0.7$ to $1.3$), ``Asian only'' identity decreases from 66\% to 28\%, while ``White only'' increases from 3\% to 55\%. Among WA families, ``Asian only'' decreases from 54\% to 18\%, ``Asian and White'' increases from 40\% to 62\%, and ``White only'' increases from 6\% to 20\%. Gender shows minimal effects in both family types. Parental education effects differ by family structure: among AW families, maternal college education increases ``Asian only'' identity from 51\% to 62\%, while among WA families, parental education produces virtually no change across identity categories.

Adult second-generation results (Figure \ref{fig:pp-secondgen-adults-aw-wa}) show similar patterns. Among AW families (Panel \ref{subfig:pp-secgen-aw-bias}), as bias increases from minimum to maximum levels, ``White only'' identity increases from 12\% to 39\%, while ``Asian and White'' decreases from 46\% to 16\%. Among WA families (Panel \ref{subfig:pp-secgen-wa-bias}), ``White only'' increases from 27\% to 38\%, ``Asian and White'' increases from 25\% to 40\%, and ``Asian only'' decreases from 47\% to 22\%. Gender shows minimal effects on identity choices for both family types.

\textbf{Third-Generation Subsample by Grandparent Composition.} Third-generation identity choices vary systematically with the number of Asian grandparents (Figures \ref{fig:pp-third-one}, \ref{fig:pp-third-two}, and \ref{fig:pp-third-three}). Anti-Asian bias produces dramatically different effects across ancestral compositions. Those with one Asian grandparent show modest responses to bias, with ``Asian only'' decreasing from 11\% to 3\% and ``Asian and White'' increasing from 34\% to 48\% as bias moves from minimum to maximum. Those with two Asian grandparents show stronger effects, with ``Asian only'' decreasing from 48\% to 13\% and ``White only'' increasing from 21\% to 49\%. Those with three Asian grandparents maintain high ``Asian only'' identification ($\approxeq 95\%$) until bias reaches its highest levels, when it drops 20 percentage points.

Gender effects are minimal across all grandparent types, with males and females showing similar identity distributions. Parental education operates differently by ancestral composition: maternal college education has modest effects among those with one grandparent, strongest effects among those with two grandparents (increasing ``Asian only'' from 18\% to 23\%), and significant effects among those with three grandparents (increasing ``Asian only'' from 88\% to 96\%).

@@

Using multinomial logit analysis, I show that anti-Asian bias fundamentally reshapes racial identity. When bias increases from minimum to maximum levels, the probability of reporting ``Asian only'' identity decreases dramatically from 98\% to 48\%, while ``White only'' identity increases from 1\% to 43\%. These strategic identity choices are most pronounced among mixed-race families, where high bias environments drive substantial shifts toward White racial identity among Asian father-White mother families and toward multiracial identity among White father-Asian mother families.

>>>>

Multinomial logit analyses reveal that anti-Asian bias fundamentally reshapes racial identity choices. I find that when bias increases from its lowest to highest levels, individuals dramatically shift away from ``Asian only'' racial identity, with probabilities decreasing from 90\% to 61\% across all generations, while probabilities of choosing ``White only'' racial identity rise from 5\% to 24\%. In contrast, I find that parental education produces modest and inconsistent effects that vary by family composition: maternal college education increases Asian identity reporting by approximately 11 percentage points among second-generation children of Asian father-White mother families but shows minimal effects in White father-Asian mother families, while paternal education effects remain small across both family types. These patterns suggest that anti-Asian bias, rather than socioeconomic factors, primarily drives identity choices, causing research using subjective measures to misestimate Asian-White gaps in highly prejudiced areas.

@@

This section presents results from the multinomial logit analysis, revealing how anti-Asian bias differentially affects the probability of choosing ``Asian only,'' ``White only,'' or ``Asian and White'' racial identity. The effects prove particularly pronounced among mixed-race Asian Americans, on whom I focus the discussion. Because multinomial logit models express coefficients in log-odds form, I present predicted probabilities that show how the likelihood of each identity choice varies with anti-Asian bias levels and other characteristics.\footnote{The online appendix presents marginal effects results for all regressions in Figures \ref{fig:marginal-effects-all}--\ref{fig:marginal-effects-third-grandparental}.}

\textbf{Overall Patterns Among All Generations.} Figure \ref{fig:pp-all-gen} presents predicted probabilities from the multinomial logit model across all generations. Anti-Asian bias strongly influences racial identity choices. As bias increases from its lowest level ($-0.7$) to its highest level ($1.3$), the predicted probability of reporting ``Asian only'' identity decreases dramatically from 90\% to 61\%, ``White only'' identity increases from 5\% to 24\%, and ``Asian and White'' identity increases modestly from 4\% to 13\%. At anti-Asian bias levels exceeding 1, the three identity categories converge to roughly equal probabilities. In contrast, gender and parental education exert minimal influence on racial identity choices: male and female respondents demonstrate virtually identical probabilities across all categories, and parental college education produces small, inconsistent effects across identity choices.

\textbf{Second-Generation Subsample by Parental Composition.} Parental composition reveals substantial differences between Asian father-White mother (AW) and White father-Asian mother (WA) families (Figures \ref{fig:pp-second-aw} and \ref{fig:pp-second-wa}). Among AW families, as bias increases from minimum to maximum levels ($-0.7$ to $1.3$), ``Asian only'' identity decreases from 63\% to 31\%, while ``White only'' increases from 5\% to 46\%. Among WA families, ``Asian only'' decreases from 50\% to 23\%, ``Asian and White'' increases from 41\% to 50\%, and ``White only'' increases from 9\% to 26\%. At the highest bias levels, the three identity categories converge to roughly equal probabilities among individuals of Asian ancestry.

Gender exerts minimal effects in both family types. Parental education operates differently by family structure. Among AW families, maternal college education increases the probability of reporting ``Asian only'' and decreases the probability of reporting ``White only.'' Paternal college education increases the probability of reporting ``Asian and White'' and decreases the probability of reporting ``Asian only.'' Among WA families, maternal education produces virtually no change across identity categories, while paternal college education increases the probability of reporting ``Asian and White'' identity and decreases the probability of reporting ``White only'' identity.

Adult second-generation results (Figures \ref{fig:pp-secondgen-adults-aw-wa} and \ref{fig:pp-secondgen-adults-aw-wa-2}) reveal similar patterns, though with greater imprecision. Among AW families (Panel \ref{subfig:pp-secgen-aw-bias}), as bias increases from minimum to maximum levels, ``White only'' identity increases from 10\% to 40\%, ``Asian and White'' decreases from 45\% to 16\%, and ``Asian only'' identity remains stable at around 45\%. Among WA families (Panel \ref{subfig:pp-secgen-wa-bias}), ``White only'' increases from 28\% to 38\%, ``Asian and White'' increases from 22\% to 42\%, and ``Asian only'' decreases from 49\% to 18\%. Gender exerts minimal effects on identity choices for both family types.

For adults, I observe years of education and family income, allowing examination of how these variables affect identity choices. Among AW families, higher education increases the probability of reporting ``Asian only'' identity and decreases the probability of reporting ``White only'' and ``Asian and White'' identities. Higher family income increases the probability of reporting ``Asian only,'' though wide confidence intervals prevent distinguishing this from ``White only'' and ``Asian and White'' reporting. Among WA families, higher education increases the probability of reporting ``Asian only'' identity and significantly decreases the probability of reporting ``White only.'' At high education levels (10 years+), confidence intervals for all three identity choices overlap, indicating imprecision. Family income exerts no discernible effect among WA families.

\textbf{Third-Generation Subsample by Grandparent Composition.} Third-generation identity choices vary systematically with the number of Asian grandparents (I show the predicted probabilities in Figures \ref{fig:pp-third-one} and \ref{fig:pp-third-two} for third-generation native-born immigrants of Asian ancestry with one and two Asian born grandparents). Anti-Asian bias produces dramatically different effects across ancestral compositions. Those with one Asian grandparent show modest responses to bias, reporting ``White only'' and ``Asian and White'' identities with equal frequency, both significantly exceeding ``Asian only'' identity. Those with two Asian grandparents report all three identities with equal probability at all anti-Asian bias levels.

Gender effects are minimal across all grandparent types, with males and females showing similar identity distributions. Parental education operates differently by ancestral composition. Among third-generation individuals with Asian ancestry and one Asian grandparent, maternal college education decreases the probability of reporting ``White only'' and increases the probability of reporting ``Asian and White'' identity, while exerting no significant effect on reporting ``Asian only'' identity. Paternal college education decreases the probability of reporting ``Asian only'' identity. Among third-generation individuals with Asian ancestry and two Asian grandparents, maternal college education increases the probability of reporting ``Asian only'' identity while exerting no significant effect on reporting ``White only'' and ``Asian and White'' identities. Paternal college education increases the probability of reporting ``Asian and White'' identity, decreases the probability of reporting ``White only'' identity, and exerts no significant effect on reporting ``Asian only'' identity.

The multinomial logit analysis demonstrates that anti-Asian bias significantly influences racial identity choices among individuals with Asian ancestry. Those facing higher bias levels distance themselves from Asian identity. Parental education (and own education among adults) shapes identity choices, particularly among mixed-ancestry individuals. Among native-born second-generation adults with Asian ancestry, higher income and education increase the likelihood of maintaining Asian racial identity, suggesting that socioeconomic status influences identity retention. These results highlight the complex interplay between external social pressures and individual characteristics in shaping racial identity decisions. Furthermore, they provide evidence that studies relying on self-reported racial identity may overestimate Asian American success and underestimate assimilation speed, as more successful individuals retain their Asian identity.

@@

Using multinomial logit analysis, I show that anti-Asian bias fundamentally reshapes racial identity. When bias increases from minimum to maximum levels, the probability of reporting ``Asian only'' identity decreases dramatically from 90\% to 61\%, while ``White only'' identity increases from 5\% to 24\%. These strategic identity choices are most pronounced among mixed-race families, where high bias environments drive substantial shifts toward White racial identity among Asian father-White mother families and toward multiracial identity among White father-Asian mother families.

### 2025-11-17 submissions/03-jpam-RR/manuscript_online_appendix.tex
....
Finish bootstrapping and incorporating the results into the main text

\begin{figure}[H]
    \centering
    \caption{Scatter Plot of Proportion Subjectively Asian on Bias}
    \label{scatter-plot-1}
    \begin{subfigure}{.9\textwidth}
    \caption{Year < 2015}
    \centering
    \includegraphics[width=.9\linewidth]{scatter-plot-bias-Asian-less2015.png}
    \end{subfigure}
    \centering
    %Second graph
    \begin{subfigure}{.9\textwidth}
    \caption{Year $\geq$ 2015}
    \centering
    \includegraphics[width=.9\linewidth]{scatter-plot-bias-Asian-great2015.png}
    \end{subfigure}
    \caption*{\footnotesize{Here are two scatter plots showing the relationship between bias and subjective Asian population in a state. Each dot represents a state in a certain year. Percent subjectively Asian = $\frac{\# \text{Asian}}{\text{Population}}$ \\
    \emph{Source.} 2004--2021 Current Population Survey.}}
    \end{figure}

\subsection*{Using \textcite{lubotskyInterpretationRegressionsMultiple2006} to Construct Bias Index} % (fold)
\label{sub:lw-bias}
In \textcite{lubotskyInterpretationRegressionsMultiple2006}, the authors propose a method to reduce measurement error in proxies by constructing a composite index. The Lubotsky-Wittenberg (henceforth LW) consider a model where a covariate is unobserved. Therefore, they use two proxies in its place, which will have measurement error. Thus, the LW method allows researchers to use two proxies that are error-ridden.

>>>>

% Marginal Effects: All Generations (after main Multinomial Logit Model plot)
\begin{center}
\begin{figure}[!htb]
\centering
\caption{Marginal Effects of Key Covariates on Racial Identity Choice from Multinomial Logit Model (All Generations)}
\label{fig:marginal-effects-all}
\includegraphics[width=0.9\linewidth]{boot_me_all_generations.png}
\caption*{\footnotesize{This figure displays the marginal effects of key covariates on the probability of each racial identification outcome, estimated from equation (\ref{eq:multinomial_logit}) using a multinomial logit model. Marginal effects represent the change in predicted probability for a one-unit increase in the covariate (or discrete change from 0 to 1 for binary variables), holding other variables at their sample means. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. Each point reports the median marginal effect across 1{,}000 bootstrap resamples, and 95\% confidence intervals come from the associated bootstrap percentile bounds. The sample includes first-, second-, and third-generation Asian Americans as defined above.}}
\end{figure}
\end{center}

% Marginal Effects: Second Generation by Parental Type (AW and WA)
\begin{center}
\begin{figure}[!htb]
\centering
\caption{Marginal Effects of Key Covariates on Racial Identity Choice by Parental Ancestry (Second-Generation Asian Americans)}
\label{fig:marginal-effects-second-parental}

\begin{subfigure}{.48\textwidth}
\caption{Asian Father-White Mother (AW)}\label{subfig:meaw}
\centering
\includegraphics[width=1\linewidth]{boot_me_second_AW.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{White Father-Asian Mother (WA)}\label{subfig:mewa}
\centering
\includegraphics[width=1\linewidth]{boot_me_second_WA.png}
\end{subfigure}

\caption*{\footnotesize{This figure displays the marginal effects of key covariates on the probability of each racial identification outcome, estimated from equation (\ref{eq:multinomial_logit}) using multinomial logit models for second-generation Asian Americans by parental ancestry configuration. Marginal effects represent the change in predicted probability for a one-unit increase in the covariate (or discrete change from 0 to 1 for binary variables), holding other variables at their sample means. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. Each point corresponds to the median marginal effect across 1{,}000 bootstrap resamples, with 95\% percentile confidence intervals. Second-generation Asian Americans are native-born individuals with at least one Asian-born parent.}}
\end{figure}
\end{center}

% Marginal Effects: Second Generation by Parental Type (AW and WA)
\begin{center}
\begin{figure}[!htb]
\centering
\caption{Marginal Effects of Key Covariates on Racial Identity Choice by Parental Ancestry (Adult Second-Generation Asian Americans)}
\label{fig:marginal-effects-second-adults}

\begin{subfigure}{.48\textwidth}
\caption{Asian Father-White Mother (AW)}
\centering
\includegraphics[width=1\linewidth]{logit_boot_me_second_AW_adults_multinom.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{White Father-Asian Mother (WA)}
\centering
\includegraphics[width=1\linewidth]{logit_boot_me_second_WA_adults_multinom.png}
\end{subfigure}

\caption*{\footnotesize{This figure displays the marginal effects of key covariates on the probability of each racial identification outcome, estimated from equation (\ref{eq:multinomial_logit}) using multinomial logit models for second-generation adults with Asian father/White mother (AW) and White father/Asian mother (WA). Marginal effects represent the change in predicted probability for a one-unit increase in the covariate (or discrete change from 0 to 1 for binary variables), holding other variables at their sample means. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. Each point corresponds to the median marginal effect across 1{,}000 bootstrap resamples, with 95\% percentile confidence intervals. Second-generation Asian Americans are native-born individuals with at least one Asian-born parent.}}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[!htb]
\centering
\caption{Marginal Effects of Key Covariates on Racial Identity Choice by Number of Asian Grandparents (Third-Generation Asian Americans)}
\label{fig:marginal-effects-third-grandparental}
\begin{subfigure}{.45\textwidth}
\caption{One Asian Grandparent}\label{subfig:oneasiangrand}
\centering
\includegraphics[width=1\linewidth]{boot_me_third_oneAsian.png}
\end{subfigure}
\hfill
\begin{subfigure}{.45\textwidth}
\caption{Two Asian Grandparents}\label{subfig:twoasiangrand}
\centering
\includegraphics[width=1\linewidth]{boot_me_third_twoAsian.png}
\end{subfigure}

\caption*{\footnotesize{This figure displays the marginal effects of key covariates on the probability of each racial identification outcome, estimated from equation (\ref{eq:multinomial_logit}) using multinomial logit models for third-generation Asian Americans by number of Asian grandparents. Marginal effects represent the change in predicted probability for a one-unit increase in the covariate (or discrete change from 0 to 1 for binary variables), holding other variables at their sample means. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. Each estimate is the median across 1{,}000 bootstrap resamples, and 95\% percentile confidence intervals accompany every point.}}
\end{figure}
\end{center}

\begin{figure}[H]
    \centering
    \caption{Scatter Plot of Proportion Subjectively Asian on Bias}
    \label{scatter-plot-1}
    \begin{subfigure}{.9\textwidth}
    \caption{Year < 2015}
    \centering
    \includegraphics[width=.9\linewidth]{scatter-plot-bias-Asian-less2015.png}
    \end{subfigure}
    \centering
    %Second graph
    \begin{subfigure}{.9\textwidth}
    \caption{Year $\geq$ 2015}
    \centering
    \includegraphics[width=.9\linewidth]{scatter-plot-bias-Asian-great2015.png}
    \end{subfigure}
    \caption*{\footnotesize{Here are two scatter plots showing the relationship between bias and subjective Asian population in a state. Each dot represents a state in a certain year. Percent subjectively Asian = $\frac{\# \text{Asian}}{\text{Population}}$ \\
    \emph{Source.} 2004--2021 Current Population Survey.}}
    \end{figure}    
\subsection*{Using \textcite{lubotskyInterpretationRegressionsMultiple2006} to Construct Bias Index} % (fold)
\label{sub:lw-bias}
In \textcite{lubotskyInterpretationRegressionsMultiple2006}, the authors propose a method to reduce measurement error in proxies by constructing a composite index. The Lubotsky-Wittenberg (henceforth LW) consider a model where a covariate is unobserved. Therefore, they use two proxies in its place, which will have measurement error. Thus, the LW method allows researchers to use two proxies that are error-ridden.

### 2025-11-17 submissions/03-jpam-RR/manuscript_tab_fig.tex
Finish bootstrapping and incorporating the results into the main text

% \pagebreak
% \newpage

% % Marginal Effects: All Generations (after main Multinomial Logit Model plot)
% \begin{center}
% \begin{figure}[!htb]
% \centering
% \caption{Marginal Effects of Key Covariates on Racial Identity Choice from Multinomial Logit Model (All Generations)}
% \label{fig:marginal-effects-all}
% \includegraphics[width=0.9\linewidth]{boot_me_all_generations.png}
% \caption*{\footnotesize{This figure displays the marginal effects of key covariates on the probability of each racial identification outcome, estimated from equation (\ref{eq:multinomial_logit}) using a multinomial logit model. Marginal effects represent the change in predicted probability for a one-unit increase in the covariate (or discrete change from 0 to 1 for binary variables), holding other variables at their sample means. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. Each point reports the median marginal effect across 1{,}000 bootstrap resamples, and 95\% confidence intervals come from the associated bootstrap percentile bounds. The sample includes first-, second-, and third-generation Asian Americans as defined above.}}
% \end{figure}
% \end{center}

@@

% % Marginal Effects: Second Generation by Parental Type (AW and WA)
% \begin{center}
% \begin{figure}[!htb]
% \centering
% \caption{Marginal Effects of Key Covariates on Racial Identity Choice by Parental Ancestry (Second-Generation Asian Americans)}
% \label{fig:marginal-effects-second-parental}

% \begin{subfigure}{.48\textwidth}
% \caption{Asian Father-White Mother (AW)}\label{subfig:meaw}
% \centering
% \includegraphics[width=1\linewidth]{boot_me_second_AW.png}
% \end{subfigure}
% \hfill
% \begin{subfigure}{.48\textwidth}
% \caption{White Father-Asian Mother (WA)}\label{subfig:mewa}
% \centering
% \includegraphics[width=1\linewidth]{boot_me_second_WA.png}
% \end{subfigure}

% \caption*{\footnotesize{This figure displays the marginal effects of key covariates on the probability of each racial identification outcome, estimated from equation (\ref{eq:multinomial_logit}) using multinomial logit models for second-generation Asian Americans by parental ancestry configuration. Marginal effects represent the change in predicted probability for a one-unit increase in the covariate (or discrete change from 0 to 1 for binary variables), holding other variables at their sample means. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. Each point corresponds to the median marginal effect across 1{,}000 bootstrap resamples, with 95\% percentile confidence intervals. Second-generation Asian Americans are native-born individuals with at least one Asian-born parent.}}
% \end{figure}
% \end{center}

% \pagebreak
% \newpage

% =========================
% 41: Multinomial Model - Predicted Probabilities (Adults, AW/WA)
% =========================
\begin{center}
\begin{figure}[!htb]
\centering
\caption{Multinomial Logit Model: Predicted Probabilities of Racial Identity Choice by Key Covariates (Second Generation Adults, AW/WA)}
\label{fig:pp-secondgen-adults-aw-wa}

@@

@@

@@

\begin{center}
\begin{figure}[!htb]
\centering
\caption{Multinomial Logit Model: Predicted Probabilities of Racial Identity Choice by Key Covariates (Third-Generation Asian Americans with Three Asian Grandparents)}
\label{fig:pp-third-three}

\begin{subfigure}{.48\textwidth}
\caption{Anti-Asian Bias}
\centering
\includegraphics[width=1\linewidth]{boot_pp_third_threeAsian_value.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{Female}
\centering
\includegraphics[width=1\linewidth]{boot_pp_third_threeAsian_Female.png}
\end{subfigure}

\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Mother}
\centering
\includegraphics[width=1\linewidth]{boot_pp_third_threeAsian_MomGradCollege.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Father}
\centering
\includegraphics[width=1\linewidth]{boot_pp_third_threeAsian_DadGradCollege.png}
\end{subfigure}

\caption*{\footnotesize{This figure shows predicted probabilities from estimating equation (\ref{eq:multinomial_logit}) using a multinomial logit model for the subsample of third-generation Asian Americans with three Asian grandparents. The model estimates the probability of choosing ``Asian only'', ``White only'', or ``Asian and White'' racial identification as a function of anti-Asian bias, gender, and parental education. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. All other variables are held at their sample means. Reported curves depict the median predicted probability across 1{,}000 bootstrap resamples, with 95\% percentile confidence intervals from the same draws.}}
\end{figure}
\end{center}

% Marginal Effects: Third Generation by Grandparental Type (One, Two, Three Asian Grandparents)
% \begin{center}
% \begin{figure}[!htb]
% \centering
% \caption{Marginal Effects of Key Covariates on Racial Identity Choice by Number of Asian Grandparents (Third-Generation Asian Americans)}
% \label{fig:marginal-effects-third-grandparental}
% \begin{subfigure}{.45\textwidth}
% \caption{One Asian Grandparent}\label{subfig:oneasiangrand}
% \centering
% \includegraphics[width=1\linewidth]{boot_me_third_oneAsian.png}
% \end{subfigure}
% \hfill
% \begin{subfigure}{.45\textwidth}
% \caption{Two Asian Grandparents}\label{subfig:twoasiangrand}
% \centering
% \includegraphics[width=1\linewidth]{boot_me_third_twoAsian.png}
% \end{subfigure}

% \begin{subfigure}{.45\textwidth}
% \caption{Three Asian Grandparents}\label{subfig:threeasiangrand}
% \centering
% \includegraphics[width=1\linewidth]{boot_me_third_threeAsian.png}
% \end{subfigure}
% \caption*{\footnotesize{This figure displays the marginal effects of key covariates on the probability of each racial identification outcome, estimated from equation (\ref{eq:multinomial_logit}) using multinomial logit models for third-generation Asian Americans by number of Asian grandparents. Marginal effects represent the change in predicted probability for a one-unit increase in the covariate (or discrete change from 0 to 1 for binary variables), holding other variables at their sample means. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. Each estimate is the median across 1{,}000 bootstrap resamples, and 95\% percentile confidence intervals accompany every point.}}
% \end{figure}
% \end{center}

% \pagebreak
% \newpage

>>>>

@@

% =========================
% 41: Multinomial Model - Predicted Probabilities (Adults, AW/WA)
% =========================
\begin{center}
\begin{figure}[!htb]
\centering
\caption{Multinomial Logit Model: Predicted Probabilities of Racial Identity Choice by Anti-Asian Bias and Gender (Second Generation Adults, AW/WA)}
\label{fig:pp-secondgen-adults-aw-wa}

@@

\begin{center}
\begin{figure}[!htb]
\centering
\caption{Multinomial Logit Model: Predicted Probabilities of Racial Identity Choice by Years of Education and Income (Second Generation Adults, AW/WA)}
\label{fig:pp-secondgen-adults-aw-wa-2}

% Top row: EducYears
\begin{subfigure}{.48\textwidth}
\caption{Years of Education (AW)}
\centering
\includegraphics[width=1\linewidth]{logit_boot_pp_second_AW_adults_multinom_EducYears.png}\label{subfig:pp-secgen-aw-EducYears}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{Years of Education (WA)}
\centering
\includegraphics[width=1\linewidth]{logit_boot_pp_second_WA_adults_multinom_EducYears.png}\label{subfig:pp-secgen-wa-EducYears}
\end{subfigure}

% Second row: lnftotval
\begin{subfigure}{.48\textwidth}
\caption{Log Family Income (AW)}
\centering
\includegraphics[width=1\linewidth]{logit_boot_pp_second_AW_adults_multinom_lnftotval.png}\label{subfig:pp-secgen-aw-lnftotval}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{Log Family Income (WA)}
\centering
\includegraphics[width=1\linewidth]{logit_boot_pp_second_WA_adults_multinom_lnftotval.png}\label{subfig:pp-secgen-wa-lnftotval}
\end{subfigure}

\caption*{\footnotesize{Predicted probabilities from multinomial logit models for second-generation adults with Asian father/White mother (AW) and White father/Asian mother (WA). Each panel shows the probability of choosing each racial identity as a function of total years of education or log family income, holding other covariates at their means. Curves plot the median predicted probability across 1{,}000 bootstrap resamples, with 95\% confidence intervals given by the bootstrap percentile bounds.}}
\end{figure}
\end{center}

% =========================
% Multinomial Model - Predicted Probabilities Third Gens
% =========================

@@

% \begin{center}
% \begin{figure}[!htb]
% \centering
% \caption{Multinomial Logit Model: Predicted Probabilities of Racial Identity Choice by Key Covariates (Third-Generation Asian Americans with Three Asian Grandparents)}
% \label{fig:pp-third-three}

% \begin{subfigure}{.48\textwidth}
% \caption{Anti-Asian Bias}
% \centering
% \includegraphics[width=1\linewidth]{boot_pp_third_threeAsian_value.png}
% \end{subfigure}
% \hfill
% \begin{subfigure}{.48\textwidth}
% \caption{Female}
% \centering
% \includegraphics[width=1\linewidth]{boot_pp_third_threeAsian_Female.png}
% \end{subfigure}

% \begin{subfigure}{.48\textwidth}
% \caption{College Graduate: Mother}
% \centering
% \includegraphics[width=1\linewidth]{boot_pp_third_threeAsian_MomGradCollege.png}
% \end{subfigure}
% \hfill
% \begin{subfigure}{.48\textwidth}
% \caption{College Graduate: Father}
% \centering
% \includegraphics[width=1\linewidth]{boot_pp_third_threeAsian_DadGradCollege.png}
% \end{subfigure}

% \caption*{\footnotesize{This figure shows predicted probabilities from estimating equation (\ref{eq:multinomial_logit}) using a multinomial logit model for the subsample of third-generation Asian Americans with three Asian grandparents. The model estimates the probability of choosing ``Asian only'', ``White only'', or ``Asian and White'' racial identification as a function of anti-Asian bias, gender, and parental education. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. All other variables are held at their sample means. Reported curves depict the median predicted probability across 1{,}000 bootstrap resamples, with 95\% percentile confidence intervals from the same draws.}}
% \end{figure}
% \end{center}

@@

### 2025-11-17 submissions/03-jpam-RR/manuscript_title_etc.tex
Finish bootstrapping and incorporating the results into the main text

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 5. Define Abstract
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\PAPERABSTRACT}{
I study the determinants of the choice to identify as Asian among those who could—those whose parents, grandparents, or selves were born in an Asian country. Using a multiple proxy regression approach, I construct a bias measure based on the Implicit Association Test (IAT), the American National Election Studies (ANES), and hate crimes against Asians. I find that individuals with Asian ancestry are significantly less likely to self-identify as Asian if they live in states with high levels of bias. A one standard deviation increase in bias decreases self-reported Asian identity by 9 percentage points across all generations. The effects vary by generation and family type: bias decreases Asian racial identity by 5 percentage points among first-generation immigrants (statistically insignificant), 8 percentage points among second-generation, and 8 percentage points among third-generation Asian Americans. Mixed-race families show the strongest responses, with bias decreasing Asian racial identity by 15 percentage points among children of Asian fathers and White mothers, and 10 percentage points among children of White fathers and Asian mothers. Using multinomial logit regression, I find that high bias environments drive substantial shifts from ``Asian only'' to ``White only'' racial identity, with probabilities changing by up to 50 percentage points. Higher parental education and income generally increase the probability of reporting Asian identity, with particularly strong effects among mixed-race children. These findings have implications for the interpretation of research on racial and ethnic gaps in economic outcomes and accurate population measurement. \PAPERJEL}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 5. Define Abstract
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\PAPERABSTRACT}{
I study the determinants of the choice to identify as Asian among those who could—those whose parents, grandparents, or selves were born in an Asian country. Using a multiple proxy regression approach, I construct a bias measure based on the Implicit Association Test (IAT), the American National Election Studies (ANES), and hate crimes against Asians. I find that individuals with Asian ancestry are significantly less likely to self-identify as Asian if they live in states with high levels of bias. A one standard deviation increase in bias decreases self-reported Asian identity by 9 percentage points across all generations. The effects vary by generation and family type: bias decreases Asian racial identity by 5 percentage points among first-generation immigrants (statistically insignificant), 8 percentage points among second-generation, and 8 percentage points among third-generation Asian Americans. Mixed-race families show the strongest responses, with bias decreasing Asian racial identity by 15 percentage points among children of Asian fathers and White mothers, and 10 percentage points among children of White fathers and Asian mothers. Using multinomial logit regression, I find that high bias environments drive substantial shifts from ``Asian only'' to ``White only'' racial identity, with probabilities changing by up to 30 percentage points. Higher parental education and income generally increase the probability of reporting Asian identity, with particularly strong effects among mixed-race children. These findings have implications for the interpretation of research on racial and ethnic gaps in economic outcomes and accurate population measurement. \PAPERJEL}
